Dear Editors,
 We are submitting our manuscript "Maximizing Torque on a Rigid Body by Pushing, Using Many Particles Steered by Shared Control Inputs", to be considered for publishing in IEEE Transaction on Automation Science and Engineering  (T-ASE). Authors are Shiva Shahrokhi, Lillian Lin, and Aaron T. Becker.

This paper springboards from the content of a preliminary conference paper, extending its substance and providing full details in a single journal paper. This paper is in IEEE International Conference on Automation Science and Engineering  (CASE), 2016, pp. 561--566. That paper covered techniques for orientation control of an object pushed by a swarm of particles, when the particles all have the same shared control input.
This paper provides analytical models and optimal solutions for three common swarm distributions, and new hardware experiments.

The primary Methodology is 3. Materials/Parts Handling and secondary Methodology is 9. Theoretical Foundations.
The primary Application is I. Construction and secondary Application is C. Healthcare and Life sciences.

We believe that the topic is a perfect fit for the scope of your journal and are hopeful that editors and reviewers share the opinion that this submission will be of interest to the readers of IEEE Transaction on Automation Science and Engineering.

With Best Regards,
Shiva Shahrokhi (on behalf of all authors)
713 743 6671, sshahrokhi2@uh.edu.
PhD Candidate, Electrical and Computer Engineering, University of Houston