
% acknowledgements for thesis

%This is where you offer thanks to anyone you feel deserves it.


I thank God that I spent some of my best years during the Ph.D. program at the University of Houston. I grew up and became more capable. I would like to take this opportunity to express my gratitude to those who were part of this journey.First, I would like to express my appreciation to my advisor, Dr. Aaron T. Becker. I truly appreciate his support, kindness, intellectual comments and caring for not only about my research but also many aspects of my life. Dr. Becker was a perfect match for me as an advisor. He is a nice person and full of energy and he makes the lab a happy and energetic place. I thank him for everything he has done for me.I would like to thank my dissertation committee members: Dr. Lydia Kavraki, Dr. David Mayerich, Dr. Rose Faghih, Dr. Stanko Brankovic and Dr. Nicaolas Tsekos for their insightful comments and suggestions and their kindness and supportiveness. I also enjoyed their classes and learned a lot from them.I was very fortunate to be the first student of swarm control lab. I am thankful to my great collaborators: Lillian Lin, Arun Mahadev, Mable Wan, Chris Ertel, Jingang Shi, and Benedict Isichei. I have always benefited from our discussions. I also would like to thank my other fabulous lab mates: Mary Burbage, Haoran Zhao, Julien Leclerc, Li Huang, Sheryl Manzoor, Mohammad Sultan, An Nguyen, Shriya Bhatnagar, Daniel Bao, Srikanth K.V.S, Parth Joshi, Javier Garcia, Steban Soto, Victor Montano, and Jarret Lonsford. I enjoyed being with all of them.I would also like to express my sincere appreciation to my parents, Nasrin and Hadi. Their belief in me made me brave enough to go for my dreams. I appreciate them for my whole life. I miss my father who was a great role model for me so much and hope he rests in peace. I believe he is looking at me and hope that I have made him proud. I am very fortunate to have my mother and deeply appreciate her encouragement and self-sacrifice for me. I also like to thank my brothers and my sister, Ali, Amir and Shima, who always backed me up and encouraged me. I appreciate them all for being such a great family.Finally, I would like to express my most gratitude and appreciation to the love of my life, my husband, Ali. I cannot imagine how I could finish my Ph.D. if he was not there to encourage and support me. Each dark day he was there to show me the tiny light at the end of the road. Each bright day he was there to make my smile bigger and make my heart warmer. He made the path possible for me, and never left me alone in the path. He is smart and hardworking and looking at him motivated me to work smarter and harder. I am forever grateful for each and every day of my life with him.


%I would like to thank my thesis committee members. I appreciate all the insightful comments Prof. Lydia Kavraki made for me. I also thank her for the great class I had with her where I enjoyed so much and had unique experiences. I appreciate all the insightful suggestions Dr. David Mayerich and Dr. Rose Faghih made and their kindness and supportiveness. I appreciate Dr. Stanko Brankovic's insightful suggestions and comments and my other wonderful class I had with him where I enjoyed and learned many things I did not know before.